\documentclass{article}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}


\newtheorem*{conjecture}{Conjecture}
\newtheorem*{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem*{proposition}{Proposition}


\makeatletter
\newcommand*{\rom}[1]{\expandafter\@slowromancap\romannumeral #1@}
\makeatother


\begin{document}

\section*{Exercise 1}

There are 11 letters in the word "MISSISSIPPI" in total. We have one M, four I's and S's and two P's. We have
eleven positions available for every letter. Moreover, we can sequentially
choose next rearrangments eliminating available positions until we exhaust all places for the letters. We have then:
\begin{equation*}
    \binom{11}{4} \cdot \binom{7}{4} \cdot \binom{3}{2} \cdot \binom{11}{4} = \frac{11!}{4! 4! 2! 1!} = 34650
\end{equation*}

To double check our reasoning, let's look at the problem from an equivalent perspective. There are \(11!\) possibilites
of rearranging 11 objects in a row where order matters. We can divide this number by respectively \(4!\), \(4!\), \(2!\) and \(1!\)
treating these factorials as a number of ways every letter could rearrange itself. By doing that we adjust for overcounting
and we end up with the right side of the above equation:
\begin{equation*}
    \frac{11!}{4! 4! 2! 1!} = 34650
\end{equation*}

\section*{Exercise 4}
\subsection*{(a)}
The total number of matches played:

\begin{equation*}
    \binom{n}{2} = \frac{n!}{2!(n - 2)!} = \frac{n(n-1)(n-2)!}{2!(n-2)!} = \frac{n(n-1)}{2}
\end{equation*}
we can do a quick sanity check to see that we are right. We know that there are \(n\) players so we want to choose
sets consisting of 2 elements from the set containing \(n\)-elements. On the other hand, we know that there are
\(n\) players who will play \(n-1\) matches and we divide this product by \(2\) to adjust for two possible
states of a given match: player A wins and player B loses or the opposite takes place.
To get the number of possible outcomes we put every possible match on the board and then count every state of 
a given match. Because there are two possibilites for a match we use Multiplication Rule to arrive to:
\begin{equation*}
    \underbrace{2 \cdot 2 \cdot 2 \cdot \dots }_\text{\(\binom{n}{2}\) times}
\end{equation*} 

So the total number of possible outcomes is \(2^{\binom{n}{2}}\)
\subsection*{(b)}
The total number of games played is \(\binom{n}{2} = \frac{n!}{2!(n - 2)!} = \frac{n(n-1)(n-2)!}{2!(n-2)!} = \frac{n(n-1)}{2}\).

We don't care about the order on the leaderboard, but order \emph{inside} the match
((W1, L2) is different than (L1, W2)).

\section*{Exercise 5}
\subsection*{(a)}
There are \(n\) rounds for \(2^n\) players taking place in the competition.

\subsection*{(b)}
We have \(2^n\) players taking place in the competition. Adjusting for the outcome of a given match (only one player can win)
we can divide the total number of players in a round by \(2\) to get the number of games played in a given round. Every next
round we need to start with a new number of remaining players arriving at:
\begin{equation*}
    \frac{2^n}{2} + \frac{2^{n-1}}{2} + \frac{2^{n-2}}{2} + \dots + \frac{2^1}{2} = 1 + \frac{1}{2} \sum_{i=1}^{n} 2^i
\end{equation*}

\subsection*{(c)}
There are \(2^n\) players starting the game. Looking at it from another angle, \(2^{n} - 1\) players must be eliminated
from the tournament (we subtract one because one player is the winner). This means that \(2^{n} - 1\) games
must be played to reveal the winner.
\newpage

\section*{Exercise 15}
Consider an experiment where we throw a coin. It can land either on heads or tails. We would like to throw it
\(n \geq 1\) times. We can consider \(n\) to be a number of experiments needed to estabilish a final sequence
of outcomes e.g \(HHTTHHTTH\) or \(TTTTTTTTTHHTT\) etc. Every throw there are two possibilites to happen 
so if we throw \(n\) times we get to have \(\underbrace{2 \cdot 2 \cdot 2 \cdot \dots}_\text{\(n\) times}\) possible
coin sequences. This is just applying Multiplication Rule so the final number of outcomes can be written as:
\begin{equation*}
    2^n
\end{equation*}
We can also count the possibilites by focusing on counting heads only (or tails). We know that there will be
\(n\) throws so heads can occur \(0, 1, 2, 3, \dots, n\) times. This means that we are choosing \(k \in \{0, 1, 2, 3, \dots, n\}\)
heads from \(n\) throws. So if we add upp all the possibilites for different heads outcomes we will end up knowing
the total number of all possible sequences:
\begin{equation*}
   \sum_{k=0}^{n} \binom{n}{k}
\end{equation*}

\section*{Exercise 16}
\subsection*{(a)}
\begin{equation*}
    \binom{n}{k} + \binom{n}{k-1} = \frac{n!}{k!(n-k)!} + \frac{n!}{(k-1)! (n - k + 1)!} =
\end{equation*}
\begin{equation*}
    = \frac{n!}{k(k-1)!(n-k)!} + \frac{n!}{(k-1)! (n - k + 1)(n - k + 1 - 1)!}
\end{equation*}
\begin{equation*}
    = \frac{n!}{k(k-1)!(n-k)!} + \frac{n!}{(k-1)! (n - k + 1)(n - k)!}
\end{equation*}
\begin{equation*}
    = \frac{n!}{(k-1)!(n-k)!k} + \frac{n!}{(k-1)!(n - k)!(n - k + 1)}
\end{equation*}
\begin{equation*}
    = \frac{n!(n-k+1)}{(k-1)!(n-k)!k(n-k+1)} + \frac{n!k}{(k-1)!(n - k)!(n - k + 1)k}
\end{equation*}
\begin{equation*}
    = \frac{n! ((n - k + 1) + k)}{(k-1)!(n - k)!(n - k + 1)k} = \frac{n!(n+1)}{(k-1)!(n - k)!(n - k + 1)k}
\end{equation*}
\begin{equation*}
    = \frac{(n+1)!}{(k-1)!(n - k)!(n - k + 1)k} = \frac{(n+1)!}{k!(n - k)!(n - k + 1)}
\end{equation*}
\begin{equation*}
    = \frac{(n+1)!}{k!(n - k + 1)!} = \binom{n+1}{k}
\end{equation*}
where we used the following facts:
\begin{equation*}
    n! = n \cdot (n-1)!
\end{equation*}
\begin{equation*}
    (n+1)! = (n+1)n!
\end{equation*}
\begin{equation*}
    (n -k + 1)! = (n - k + 1)(n-k)!
\end{equation*}
\subsection*{(b)}
Consider an organization consisting of \(n + 1\) people. The number of groups we can choose from our sample is \(\binom{n+1}{k}\).
Here we are treating everyone equally and we do not distinguish between people.
On the other hand, imagine that one of the people is the president of the organization (so \(n\) employees plus one president).
We can first count groups of people which won't include the president and then add the number of groups that have president
removed from them. To put it algebraically:
\begin{equation*}
   \underbrace{\binom{n}{k}}_\text{Number of groups without the president} + \underbrace{\binom{n}{k - 1}}_\text{Number of groups with the president removed}
\end{equation*}

\section*{Exercise 26}
\subsection*{(a)}

We are trying to choose a random sample of size 1000 from 1 million people. If we want to do that with replacement, then it means
there are \(1 000 000^{1000}\) possibilites of choosing our sample. This number is really large and moreover, we need to 

\subsection*{(b)}

We know that the size of our sample space is \(1 000 000^{1000}\). This number represents all possibilites for which people
can be chosen as a random sample. We also know that out of this group, \(\frac{1 000 000!}{(1 000 000 - 1000)}!\) samples will
be unique, in a sense that there will be no repetitions of residents chosen for the sample. Let's use the complement to 
calculate the probability we seek and let \(A\) be an event that any resident will not appear more than once in the sample:
\begin{equation*}
    P(A) = \frac{\frac{1000000!}{(1000000 - 1000)!}}{1000000^{1000}}
\end{equation*}
Let \(B\) be an event that at least one resident will be chosen more than once:
\begin{equation*}
    P(B) = 1 - P(A)
\end{equation*}
So our final result is:
\begin{equation*}
    P(B) = 1 - \frac{\frac{1000000!}{(1000000 - 1000)!}}{1000000^{1000}} \approx 0.393
\end{equation*}

\end{document}
